Visualizing the Geography of Genetic Variants

### 2016-07-01 paper.Rmd
upated readme and fixed typo

```{r figure3, echo=FALSE, message=FALSE, fig.height=6, fig.width=6, fig.align='center', fig.cap='Example map from the Geography of Genetic Variants web application displaying the use of varying transparency of population pie charts to represent uncertainty in allele frequencies. The transparency is scaled in proportion to the number of observed chromosomes for a particular variant in each population.'}
img <- readPNG("figures/png/figure3.png")
grid.raster(img)
```

>>>>

```{r figure3, echo=FALSE, message=FALSE, fig.height=6, fig.width=6, fig.align='center', fig.cap='Example map from the Geography of Genetic Variants web application displaying the use of varying transparency of population pie charts to represent uncertainty in allele frequencies. The transparency is scaled in proportion to the number of observed chromosomes in each population for a particular variant.'}
img <- readPNG("figures/png/figure3.png")
grid.raster(img)
```
